Inducing Domain Specific Languages for Bayesian Program Learning

### 2018-02-06 paper.tex
example invented primitives for text
at its introduction

\newcommand{\system}{\textsc{HelmholtzHacker}~}
\newcommand{\lowerBound}{\mathscr{L}}
% Use the following line for the initial blind version submitted for review:
\usepackage{icml2018}

@@

This work proposes \emph{learning} DSLs.
We consider the problem of solving many related program induction tasks,
starting with a Lisp-like representation.
We introduce an algorithm, called the \system,
which creates its own DSL by discovering and then reusing
new useful programming idioms and subroutines.

@@

Our algorithm is best understood as inference in a hierarchical Bayesian model (Figure~\ref{graphicalModel}(a): black lines):
A DSL $\mathcal{D}$, equipped with a real-valued weight vector $\theta$,
defines a distribution over programs.
A program is sampled from $(\mathcal{D},\theta)$,
and then the program is executed to determines the agent's observations.
Our goal will be both to infer the programs that best explain our observations,
and at the same time induce a DSL
that distills the commonalities across all of the programs that solve the tasks.
%% Inducing the DSL means learning the symbolic structure of a latent programming language,
%% and so we are confronted with two distinct structure learning problems:
%% the structure of the programs and the structure of the DSL.

@@

  \centering
  \begin{tabular}{l}
  \toprule
    \texttt{0}, \texttt{+1},\texttt{-1}\\
    \texttt{split}, \texttt{join}, \texttt{map}, \texttt{length}, \texttt{slice}\\
    \texttt{append}, \texttt{chr->str}, \texttt{trim}, \texttt{index}\\
    \texttt{lowercase}, \texttt{uppercase}, \texttt{capitalize}\\
    \texttt{""},    \texttt{","},     \texttt{" "},    \texttt{"<"}, \texttt{">"}  
  \\\bottomrule
  \end{tabular}
  \caption{Initial set of primitives provided to the system for learning string editing programs}\label{textPrimitives}
  \end{table}
\begin{figure}

>>>>

\newcommand{\system}{\textsc{DreamHacker}~}
\newcommand{\lowerBound}{\mathscr{L}}
% Use the following line for the initial blind version submitted for review:
\usepackage{icml2018}

@@

This work proposes learning DSLs.
We consider the setting where we have a collection of related programming tasks,
each specified by a set of input/output examples.
Our algorithm, called \system,
does two things:
it finds programs that solve each of the tasks,
and at the same time creates its own DSL by discovering and reusing
new domain-specific subroutines.
The idea is that induced DSL
should distill the commonalities across the programs that solve the tasks,
and so can be used to solve other related program learning problems.

%% starting with a Lisp-like representation.
%% We introduce an algorithm, called the \system,
%% which creates its own DSL by discovering and then reusing
%% new useful programming idioms and subroutines.

@@

Viewed as an inference problem,
our goal is to infer the DSL, written $\mathcal{D}$,
along with a program (written $p$) for each set of inputs/outputs (\emph{tasks}, written $x$).
A DSL $\mathcal{D}$ is a collection of domain specific subroutines.
We equip $\mathcal{D}$ with a real-valued weight vector, $\theta$, and together
$(\mathcal{D},\theta)$ define a distribution over programs.
Figure~\ref{graphicalModel}(a) the diagrams this inference problem as a hierarchical Bayesian model.

%% Inducing the DSL means learning the symbolic structure of a latent programming language,
%% and so we are confronted with two distinct structure learning problems:
%% the structure of the programs and the structure of the DSL.

@@

  \centering
  \begin{tabular}{c}
    String editing primitives\\
    \begin{tabular}{l}
    \toprule
    \texttt{0}, \texttt{+1},\texttt{-1}\\
    \texttt{split}, \texttt{join}, \texttt{map}, \texttt{length}, \texttt{slice}\\
    \texttt{append}, \texttt{chr->str}, \texttt{trim}, \texttt{index}\\
    \texttt{lowercase}, \texttt{uppercase}, \texttt{capitalize}\\
    \texttt{""},    \texttt{","},     \texttt{" "},    \texttt{"<"}, \texttt{">"}  
  \\\bottomrule
    \end{tabular}\\
\\    Subset of learned DSL\\
    \begin{tabular}{l}
      \toprule
      $f_0 = $\texttt{(+ (chr->str c))}\\
      $f_1($\texttt{i,c,s}$) = $      \texttt{(+ (nth i (split c s)) (chr->str s))}\\
      $f_2($\texttt{s,c}$) = $\texttt{(}$f_0$\texttt{ c) s (}$f_1$\texttt{ c s (1+ 0))} (\emph{Extracts substring delimited by character})
    %% $f_0($\texttt{i,c,s}$) = $    \texttt{(+ (index i (split c s)) (chr->str c))}\\
    %% $f_1 = $\texttt{(join "")}
  \\\bottomrule
    \end{tabular}
  \end{tabular}
  \caption{Initial set of primitives provided to the system for learning string editing programs}\label{textPrimitives}
  \end{table}
\begin{figure}
